---
title: "Live Demo"
output: html_notebook
runtime: shiny
---

## jQuery UI and shinyjqui

`jQuery UI` is a curated set of user interface interactions, effects, widgets, and themes built on top of the jQuery JavaScript Library.

Main page: https://jqueryui.com/

`shinyjqui` is an R wrapper of jQuery UI JavaScript library. It allows users to more easily to apply jQuery UI interactions to a shiny app.

_The highlighted items have been implemented in `shinyjqui`_

* Interactions

    + [__Draggable:__](https://jqueryui.com/draggable/) Allow elements to be moved using the mouse.
    
    + [__Droppable:__](https://jqueryui.com/droppable/) Create targets for draggable elements.
    
    + [__Resizable:__](https://jqueryui.com/resizable/) Change the size of an element using the mouse
    .
    + [__Selectable:__](https://jqueryui.com/selectable/) Use the mouse to select elements, individually or in a group.
    
    + [__Sortable:__](https://jqueryui.com/sortable/) Reorder elements in a list or grid using the mouse.

* Widgets

    + Accordion, Autocomplete, Button, Checkboxradio, Controlgroup, Datepicker, Dialog, ...

* Effects

    + [__Effect:__](https://jqueryui.com/effect/) Apply an animation effect to an element.
    
    + [__Show/Hide/Toggle:__](https://jqueryui.com/show/) Display/Hide elements using custom effects.
    
    + [__Add/Remove/Switch/Toggle Class:__](https://jqueryui.com/addClass/) Adds/Removes class(es) to elements while animating all style changes.
    
    + [Easing:](https://jqueryui.com/easing/) Apply an easing equation to an animation.
    
    + [Color Animation:](https://jqueryui.com/animate/) Animate the properties of elements between colors.
    
* Utilities

    + [Position:](https://jqueryui.com/position/) Position an element relative to the window, document, another element, or the cursor/mouse.
    
    + [Widget Factory:](https://jqueryui.com/widget/) Create stateful jQuery plugins using the same abstraction as all jQuery UI widgets.


## Demo

```{r}
# Load packages:
library(shiny)
library(shinyjqui)
```

### Mouse Interactions

* `jqui_draggable()`, 
* `jqui_droppable()`, 
* `jqui_resizable()`, 
* `jqui_selectable()`, 
* `jqui_sortable()`

`jqui_xxx(ui, operation = c("enable", "disable", "destroy", "save", "load"), options = NULL)`

#### 1. Quick start:
```{r echo=TRUE}
ui <- fluidPage(
  jqui_draggable(div("=>Drag Me<="))
)

server <- function(input, output, session) {}

shinyApp(ui, server, options = list(height = 100))
```


#### 2. Operation: enable/disable :
```{r echo=TRUE}

ui <- fluidPage(
  actionButton("enable", "Enable Resizable"),
  actionButton("disable", "Disable Resizable"),
  
  plotOutput("myplot", width = 200, height = 200)
)

server <- function(input, output, session) {
  output$myplot <- renderPlot( plot(runif(10)) )
  
  observeEvent(input$enable, {
    jqui_resizable("#myplot")
  })
  
  observeEvent(input$disable, {
    jqui_resizable("#myplot", operation = "disable")
  })
}

shinyApp(ui, server, options = list(height = 300))
```
CSS Selector Reference: https://www.w3schools.com/cssref/css_selectors.asp



#### 3. Operation: save/load (within a shiny session, client-side)
```{r echo=TRUE}

ui <- fluidPage(
  actionButton("save", "Save position"),
  actionButton("restore", "Restore position"),
  
  jqui_sortable(
    tags$ul(
      id = 'lst',
      tags$li('A'),
      tags$li('B'),
      tags$li('C')
    )
  )
)

server <- function(input, output, session) {
  observeEvent(input$save, {
    jqui_sortable("#lst", operation = "save")
  })

  observeEvent(input$restore, {
    jqui_sortable("#lst", operation = "load")
  })
}

shinyApp(ui, server, options = list(height = 150))
```
Can also be applied to draggable, resizable and selectable: https://yang-tang.github.io/shinyjqui/articles/save-and-restore.html#save-and-restore-within-a-shiny-session-client-side


#### 4. Operation: save/load (across shiny sessions, bookmarking)
```{r echo=TRUE}

ui <- function(request) {
  fluidPage(
    bookmarkButton(),
    jqui_draggable(plotOutput("myplot", width = 200, height = 200))
  )
}

server <- function(input, output) {
  output$myplot <- renderPlot( plot(runif(10)) )
  jqui_bookmarking()
}

enableBookmarking(store = "url")
shinyApp(ui, server, options = list(height = 300))
```
Shiny bookmarking: https://shiny.rstudio.com/articles/bookmarking-state.html


#### 5. Options
```{r echo=TRUE}
ui <- fluidPage(
  jqui_draggable(div("=>Drag Me<="), options = list(axis = 'x'))
)

server <- function(input, output, session) {}

shinyApp(ui, server, options = list(height = 100))
```
Find more options in jqueryui document page: https://api.jqueryui.com/category/interactions/


#### 6. Shiny input values
```{r echo=TRUE}

ui <- fluidPage(
  verbatimTextOutput("dim"),
  jqui_resizable(plotOutput("myplot", width = 200, height = 200))
)

server <- function(input, output, session) {
  output$myplot <- renderPlot( plot(runif(10)) )
  
  output$dim <- renderPrint({
    input$myplot_size
  })
}

shinyApp(ui, server, options = list(height = 400))
```
More details in https://yang-tang.github.io/shinyjqui/articles/introduction.html#mouse-interactions

#### 7. Shiny widgets with mouse interactions
```{r echo=TRUE}

ui <- fluidPage(
  
  orderInput('list1', 'list1', items = month.abb, item_class = 'info'),
  
  
  orderInput('list2', 'list2 (can be moved to list1 and list4)', items = month.abb,
             connect = c('list1', 'list4'), item_class = 'primary'),
  
  
  orderInput('list3', 'list3 (can be copied to List2 and List4)', items = month.abb,
             as_source = TRUE, connect = c('list2', 'list4'), item_class = 'success'),
  
  
  orderInput('list4', 'list4 (can be moved to List2)', items = NULL, connect = 'list2',
             placeholder = 'Drag items here...')
  
)

server <- function(input, output, session) {}

shinyApp(ui, server, options = list(height = 400))
```
Other widgets: draggableModalDialog, sortableCheckboxGroupInput, sortableRadioButtons, sortableTabsetPanel, sortableTableOutput, selectableTableOutput
More about orderInput: https://yang-tang.github.io/shinyjqui/articles/orderInput.html

### Animation effects

```{r echo=FALSE}
print(get_jqui_effects())
```


```{r echo=TRUE}
server <- function(input, output) {
  
  observeEvent(input$show, {
    jqui_show('#myplot', effect = "blind")
  })
  
  observeEvent(input$hide, {
    jqui_hide('#myplot', effect = "blind")
  })
  
  output$myplot <- renderPlot( plot(runif(10)) )

}

ui <- fluidPage(

  plotOutput("myplot", width = 200, height = 200),
  actionButton('show', 'Show'),
  actionButton('hide', 'Hide')
)

shinyApp(ui, server, options = list(height = 300))
```
More about effects: https://api.jqueryui.com/category/effects/
